\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-03-01 paper.tex
[minor] toaster ref

\uwds (as well as {\sc TOASTER} (\emph{Tracking Of Agents and Spatio-TEmporal Reasoning})~\cite{milliezframework2014}) is specifically inspired by geometric and temporal reasoners like {\sc Spark}
(\emph{SPAtial Reasoning \& Knowledge})~\cite{sisbot2011situation}.{\sc Spark}
acts as a situation assessment reasoner that generates symbolic knowledge from
the geometry of the environment with respect to relations between objects,
robots and humans. It also takes into account the different perspective that
each agent has on the environment. {\sc Spark} embeds a modality-independent
geometric model of the environment that serves both as basis for the fusion of
the perception modalities and as bridge with the symbolic
layer~\cite{lemaignan2016artificial}. This geometric model is built from 3D CAD
models of the objects, furniture and robots, and full body, rigged models of
humans. It is updated at run-time by the robot's sensors.  Likewise, \uwds
embeds a grounded amodal model of the environment, updated online from the
robot's sensors (sensor fusion).

>>>>

\uwds  is specifically inspired by geometric and temporal reasoners like {\sc
Spark} (\emph{SPAtial Reasoning \& Knowledge})~\cite{sisbot2011situation} or
{\sc toaster} (\emph{Tracking Of Agents and Spatio-TEmporal
Reasoning})~\cite{milliezframework2014}. {\sc Spark} acts as a situation
assessment reasoner that generates symbolic knowledge from the geometry of the
environment with respect to relations between objects, robots and humans. It
also takes into account the different perspective that each agent has on the
environment. {\sc Spark} embeds a modality-independent geometric model of the
environment that serves both as basis for the fusion of the perception
modalities and as bridge with the symbolic layer~\cite{lemaignan2016artificial}.
This geometric model is built from 3D CAD models of the objects, furniture and
robots, and full body, rigged models of humans. It is updated at run-time by the
robot's sensors.  Likewise, \uwds embeds a grounded amodal model of the
environment, updated online from the robot's sensors (sensor fusion).
